### 2022-12-29 tesis_Rodolfo/Chapter3/chapter3.tex
Rodolfo Thesis

\chapter{ Luminometer system and calibration description}

%%%%Introduction%%%%%%%%%%%%%%%%%%%%5

A total of seven systems are used for measuring luminosity at CMS, being the PCC one of them.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Pixel Clusters and the PCC method}

Luminosity measurements at CMS are provided by the several luminometers in the detector.
Each luminometer measures the event rate by reading out a specific quantity of objects observed by the detector, These can be for example clusters, coincidences or tracks. For the TEPX luminometers these objects are pixel clusters and coincidences, using the pixel cluster counting (PCC) method to provide offline luminosity measurements. This method was one of the main source of luminosity measurements for CMS, during the 2016-2018 data taking period, and it is expected to be the same for the Phase-2 upgrade.\\
The clustering algorithm is very complex, but striping it down to the most simple example: the algorithm considers a cluster of pixels only if two hits, or more,  activate neighboring pixels horizontally, vertically or diagonally, within the same module. Figure\ref{pixclust} shows an example of this.
\begin{figure}[H]
\begin{minipage}[b]{0.5\linewidth}
\centering
\begin{tikzpicture}
    [%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
        box/.style={rectangle,draw=black,thick, minimum size=1cm},
    ]%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\foreach \x in {0,1,...,4}{
    \foreach \y in {0,1,...,4}
        \node[box] at (\x,\y){};
}

\node[box,fill=red  ] at (1,4){};  
\node[box,fill=red ] at (0,4){};  
\node[box,fill=red ] at (0,3){}; 
\node[box,fill=red  ] at (1,3){};
\end{tikzpicture}
\end{minipage}
\begin{minipage}[b]{0.5\linewidth}
\centering
\begin{tikzpicture}
    [%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
        box/.style={rectangle,draw=black,thick, minimum size=1cm},
    ]%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\foreach \x in {0,1,...,4}{
    \foreach \y in {0,1,...,4}
        \node[box] at (\x,\y){};
}

\node[box,fill=red  ] at (0,4){};  
\node[box,fill=red ] at (2,4){};  
\node[box,fill=red ] at (1,1){}; 
\node[box,fill=red ] at (4,2){}; 
\end{tikzpicture}
\end{minipage}
\caption[Pixel cluster selection algorithm]{The figure shows a representation of the pixel modules, \textit{left}: four hits (red) on four neighbouring pixels, these is considered a pixel cluster by the clustering algorithm. \textit{right}: the hits activate random pixel in the module, these will not be considered as a cluster by the clustering algorithm.}
\label{pixclust}
\end{figure}
A hit occurs when a charged particle passes through a silicon pixel, depositing an amount of energy in the pixel. The PCC method takes advantage of the high densities of pixels, and the relative low occupancy of the CMS tracker, to provide precise luminosity measurements, with good stable measurements over time. The number of pixel clusters activated, per bunch crossing, is a linear function of the number of proton-proton interactions per bunch crossing (pileup). During several zero-bias events, where the only requirement is that the bunches pass through one another on the interaction point, a mean number of pixel clusters, $\left\langle N_{\text {cluster }}\right\rangle
$,is activated:
\begin{equation}
\left\langle N_{\text {cluster }}\right\rangle\equiv\left\langle N_{\text {cluster/int}}\right\rangle\mu
\label{pcc}
\end{equation}
where $\left\langle N_{\text {cluster/int}}\right\rangle$ is the mean number of clusters activated per interaction and $\mu$ is the pileup. Using equation \ref{pileup} and \ref{pcc}, a calibration constant between the mean number of pixel cluster and the instantaneous luminosity can be defined:

\begin{equation}
    \left\langle N_{\text {cluster }}\right\rangle\equiv\frac{\sigma_{vis}}{f}\mathcal{L}_{ins}
\end{equation}
where the calibration constant, $\sigma_{vis}$, is   
\begin{equation}
    \sigma_{vis}=\sigma_{tot}\left\langle N_{\text {cluster/int}}\right\rangle
\end{equation}
The value of $\sigma_{vis}$ is determined using a van der Meer (vdM) scan, with 
\begin{equation}
    \sigma_{vis}= \frac{\left\langle N_{\text {cluster/vdM }}\right\rangle f }{\mathcal{L}_{ins/vdM}}
\end{equation}
where $\left\langle N_{\text {cluster/vdmM }}\right\rangle$ is the mean number of pixel cluster at the peak of the scan and $\mathcal{L}_{ins/vdM}$ is the instantaneous luminosity obtained in the scan \cite{CMS-PAS-LUM-12-001}.

@@

\section{Calibration using the van der Meer method }
The calibration of the luminometrs is done by performing van der Meer scans, where the goal is to determine the calibration constant $\sigma_{\text {vis}}$.\\
In practice, the normalized bunch transverse distributions of each beam is not known, thus the overlap width integrals in \ref{lumy2} cannot be solved analytically. The vdM scans determines the valued of these integrals by separating the two beams and moving them across each other while measuring the resulting rates (Figure \ref{vdm1} (left) illustrates this process)
\begin{equation}
    \int \rho_1(x)\rho_{2}(x)dx=\frac{R_{x}(0)}{\int R_{x}(\Delta x)d\Delta x}
\end{equation}
where $R_{x}(\Delta x)$ is the measured rate, when the beams are separated a distance $\Delta x$. Defining the beam overlap  width as
\begin{equation}
\Sigma_{x}=\frac{1}{\sqrt{2\pi}}\frac{\int R_{x}(\Delta x) d\Delta x}{R_{x}(0)}
\label{sigma2}
\end{equation}
doing the same can be done for $\Sigma_{y}$, equation \ref{lumy2} can be rewritten: 
\begin{equation}
    \mathcal{L}=\frac{N_1N_2N_p f}{2\pi\Sigma_x\Sigma_y}
\end{equation}
Once measurements have been taken, the rate is plotted as a function of beam separation and a Gaussian-like function is fitted to the data, as shown id Figure \ref{vdm1} (right). Using this function, the integral in equation \ref{sigma2} can be solved and the overlap width determined. Using \ref{lumy0} and \ref{lumy2} the calibration constant $\sigma_{vis}$ can be determined:
\begin{equation}
    \sigma_{vis}=\frac{2\pi \Sigma_x\Sigma_y}{N_1N_2N_p f} R_{peak}
    \label{sigmavis}
\end{equation}
where $R_{peak}$ is the measured rate at the peak of the scan \cite{CMS-PAS-LUM-18-002}\cite{CMS-PAS-LUM-12-001}. The original procedure can be found in \cite{vanderMeer:296752}.
\newcommand\gauss[2]{1/(#2*sqrt(2*pi))*exp(-((x-#1)^2)/(2*#2^2))} % Gauss function, parameters mu and sigma

\begin{figure}[ht]
\begin{minipage}[b]{0.5\linewidth}
\centering
\begin{tikzpicture}[x=.5cm,y=.5cm, scale=1.6]

\draw[<->,very thick] (-4.5,0) -- (4.5,0)node[right] {$x$};
\draw[<->,very thick] (0,-3) -- (0,3) node[above] {$ y$};

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\draw[fill=red, opacity=0.6] (0,-1.6) ellipse (4 mm and 2.5 mm);
\draw[fill=blue, opacity=0.6] (0,-2) ellipse (4 mm and 2.5 mm);

\draw[fill=red, opacity=0.6] (0,0) ellipse (4 mm and 2.5 mm);
\draw[fill=blue, opacity=0.6] (0,0) ellipse (4 mm and 2.5 mm);

\draw[fill=red, opacity=0.6] (0,1.6) ellipse (4 mm and 2.5 mm);
\draw[fill=blue, opacity=0.6] (0,2) ellipse (4 mm and 2.5 mm);

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\draw[fill=red, opacity=0.6] (-2.6,0) ellipse (4 mm and 2.5 mm);
\draw[fill=blue, opacity=0.6] (-3,0) ellipse (4 mm and 2.5 mm);

\draw[fill=red, opacity=0.6] (0,0) ellipse (4 mm and 2.5 mm);
\draw[fill=blue, opacity=0.6] (0,0) ellipse (4 mm and 2.5 mm);

\draw[fill=red, opacity=0.6] (2.6,0) ellipse (4 mm and 2.5 mm);
\draw[fill=blue, opacity=0.6] (3,0) ellipse (4 mm and 2.5 mm);
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\draw[->,]  (1,2) -- (1,0.5)node[pos=0.25, right] {\text {scan in y}};
\draw[->,]  (-3,.7) -- (-0.5,.7)node[pos=0.5, above] {\text {scan in x}};
\end{tikzpicture}
\end{minipage}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{minipage}[b]{0.5\linewidth}
\centering
\begin{tikzpicture}
\begin{axis}[every axis plot post/.append style={ color=black,
  mark=x ,domain=-4:4,samples=9,smooth,fill=blue,opacity=0.4, mark size=5pt,mark options={color=red}}, % All plots: from -2:2, 50 samples, smooth, no marks
axis x  line=bottom,very thick, % no box around the plot, only x and y axis
axis y line=left,very thick, % the * suppresses the arrow tips
enlargelimits=upper, xmin=-4.5,
xlabel=\(\Delta x/y\),
ylabel=\(Rate\),
ytick={5},xtick={5},
every axis y label/.style={
    at={(ticklabel* cs:1.05)},
    anchor=south,
},
every axis x label/.style={
    at={(ticklabel* cs:1.05)},
    anchor=west,
},] % extend the axes a bit to the right and top
\addplot[]  {\gauss{0}{2}};

\end{axis}
\draw[<->,very thick] (1.8,2.83) -- (4.8,2.83)node[pos=0.5,below] {$\Sigma_{x/y}$};
\draw[dashed,very thick] (0,5.18) -- (3.33,5.18)node[pos=0.5,below] {\text {Peak Rate}};
\end{tikzpicture}

\end{minipage}
\caption[vdM scan process.]{\textit{Left}: A diagram that shows how the two beams are scanned across the x and y axis. \textit{ Right}: An example of a Gaussian-like function (Blue), being fitted to the rate measurements (red xs) taken during a VDM scan.}
\label{vdm1}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{2018 Calibration Scan program}
The VdM scans, and other scans regarding to calibrations, were performed during the LHC fill 6868 on June 30 and July 1, 2018 at $\sqrt{s}=13TeV$. The LHC filling scheme used 124 colliding bunch pairs at the CMS interaction point (IP5) widely spread over the orbit to reduce long range beam-beam effects and detector afterglow. The resulting beam size $\sigma_{b}$ at the beginning of the fill was in the range of approximately 85–95 and 80–90 $\mu m$ in $x$ and $y$, respectively, increasing over time in the $x$ dimension and decreasing over time in the $y$ dimension.No crossing angle was used for collisions at ATLAS and CMS. The resulting peak pileup was approximately $\mu = 0.6$ , much lower than in a regular physics fill.

The bunch intensities were approximately $7-9 \times 10^{10} $ protons per filled bunch, resulting in a total beam intensity of slightly above $10^{13}$ protons per beam. The total beam intensities were measured with the DC Current Transformers (DCCT) [15], and the bunch currents were measured with the Fast Beam Current Transformers (FBCT) [16]. The beam orbit was monitored using two systems, the DOROS beam position monitors (BPMs) [17] located near IP5, and the arcBPMs located in the LHC arcs adjacent to CMS.  ***The orbit is also tracked using movements of the luminous region based on reconstructed vertices. The arc BPM measurements are translated to a beam position at IP5 using the LHC optics file; the specific optics file used for this scan is R2016c A19mC19mA19mL24.

To ensure a dataset with a high event count for PCC even at large beam separations, CMS recorded the zero-bias triggers on 5 bunch pairs (BCIDs 265, 865, 1780, 2192, and 3380) and recorded events with a total rate of $27.7kHz$.

The CMS VdM scan program was conducted in two parts (``takes''), due to an alarm. The first part consisted of a total of six x-y scan pairs. Two (``emit1'' and ``emit'') were short ``emittance'' scans, in which the two beams were separated by $4sigma_{b}$ in 9 steps with 10 seconds integration time at each scan point.***
Scan pair ``norm1'' was a standard VdM scan, in which the two beams were separated by $6\sigma_{b} \approx 600 \mu m$  and scanned across one another in a sequence of 25 steps with 30 seconds per step.

The second part of the scan program was conducted in the same fill but about $7.5$ hours later. It consisted of twelve scan pairs. Scan pair ``emit3'' was a short emittance scan, followed by scan pairs ``imag2'' and ``imag3'' of the beam imaging kind, an offset scan pair ``offset2'', and finally two normal VdM scan pairs ``norm2'' and ``norm3''. The latter two allow us to test the reproducibility of the measuremen.

****After ``norm3'' scan pair, there were the first superseparation period, in which the beams are separated a distance of $6 \sigma_{b}$ in both $x$ and $y1 direction$ for $5$ minutes long in order to get a bakcground estimation.**** source: Analyis Note 2018

A length scale calibration (LSC) was performed after scan pair ``norm3'' using two different methods. The first, ``lsc1'', was the ``constant separation'' scan, in which the two beams were separated by $1.4\sigma_{b}$ (approximately equal to $1\Sigma$) and moved together in steps of $1\sigma_{b}$ across and back, for a total of $10$ steps with $70$ seconds per step, once in each transverse direction. A second ``variable separation'' method with scan pair ``lsc2'' was also executed, in which one beam (starting with beam 1) is moved to $-2.5\sigma_{b}$ and then a three-point scan (a ``miniscan'') is performed with the other beam (starting with beam 2) at a relative position of $-1.25\sigma_{b}$, $0$, and $+ 1.25 \sigma_{b}$. The position of the first beam is then translated in five steps in the same direction to $+2.5 \sigma_{b}$, repeating the miniscan at each step. This procedure is repeated four times, with two directions for each of the two beams. Each scan point has a duration of about $46s$.

Finally, a normal VdM scan pair “norm4”,*** a second super separation period***,  and two short emittance scan pairs “emit4” and“emit5” concluded the program.

In each scan pair, the scan was performed first in the x direction and then in the y direction, with the exception of the variable separation length scale calibration scan pairs, which were done the other way around.
Figure \ref{2018sp} shows the beam positions for the two beams in the x and y directions as measured by the DOROS BPMs during the scan program, showing all 18 scan pairs.
\begin{center}
    \begin{figure}[H]
        \centering
        \includegraphics[scale=0.5]{Chapter3/2018Scanprogram.png}
        \caption[2018 San program.]{Relative change in beam positions measured by the DOROS BPMs during the 2018 scan program for the two individual beams in the horizontal x and vertical y planes, as a function of the elapsed time from the beginning of the program. The top row shows the portion ofthe scan program before the alarm at CMS, while the bottom two rows show the scan program after the alarm.[source: pas-lum-18]}
        \label{2018sp}
    \end{figure}
\end{center}

The beam imaging and offset scans are intended for specific studies on the beam shapes described in Section 4**, and they can also be analyzed as traditional van der Meer scans. Both the LSC and beam imaging scans are discussed in detail in Ref. [18**]. The offset scan data is analyzed for the first time in 2018.

source: pas-lum-18
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Corrections and systematic uncertainties}
There are several systematic effects which affect the beam overlap width measurement, and hence the $\sigma_{vis}$ is extracted from the VdM scan procedure. These effects are measured and, where applicable, corrected as described below, and a systematic uncertainty is assigned to the resulting measured cross section for each source.

Framework correction flags

\begin{itemize}
 \item ghost and satellite
 \item Background (several types, in our case from SS)
 \item Orbit drift (sep and rate)
 \item Beam Beam
 \item DynamicBeta
 \item Length Scale
 \item PeakToPeak
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Beam beam correction}
Beam beam correction:

\subsection{Veto module correction?}

>>>>

\chapter{Luminosity  Measurement and Calibration}
\label{ch3}
%%%%%%%%%%%%%%Introduction%%%%%%%%%%%%%%%%%%%%

The precision measurement of the luminosity delivered to the CMS by the LHC is important for a variety of reasons. Online, the luminosity measurement provides realtime feedback on the LHC performance and operation. Offline, the luminosity measurement is a crucial component of physics analysis, either for measuring the cross section of observed processes or for setting upper limits in searches for processes BSM \cite{pas_18}.\\
A total of seven systems are used for measuring luminosity at CMS. These systems are referred to as luminometers.  Each luminometer reads out a rate of the specific quantities observed in the detector (hits, tracks, clusters, etc.). This rate, R, should be proportional to the instantaneous luminosity,$\mathcal{L}_{inst}$, with the constant of proportionality given by the visible cross section $\sigma_{vis}$ \cite{pas_18}:

\begin{equation}
R=\mathcal{L}_{inst}\sigma_{vis}
\label{lumi_exp_gen}
\end{equation}

The determination of $\sigma_{vis}$ is carried out through van der Meer (vdM) scans performed with a dedicated LHC machine setup, exploited by S. Van der Meer for luminosity measurements at ISR \cite{vdM_cal}.

\section{Pixel Cluster Counting method}
The Pixel Cluster Counting method exploits the very large number of pixels in the tracker of the CMS detector. At design luminosity of $10^{34}cm^{-2}s^{-1}$, the detector occupancy is less than 0.1\% on average (the average number of clusters per minimum bias interaction is about 50 and the average number of pixels per cluster is about 5) \cite{pas-13}. The very low occupancy leads to an excellent linear detector response with increasing LHC luminosity \cite{pas_18}. \\
The PCC method uses the rate of pixel clusters in the CMS pixel detector to provide an offline luminosity measurement. Pixel clusters are formed from adjacent pixels, as mentioned in section \ref{pixel_clust_reco}. PCC measurement uses the data collected with the standard CMS trigger system with triggers requiring colliding bunches but not any specific event activity; this is referred as "zero-bias trigger'' \cite{pas_18}.\\
Each bunch crossing gives rise to some number of pp interactions, with each such interaction resulting in some number of pixel clusters. If the average over several zero-bias events is taken, the mean number of pixel clusters per event is \cite{PCC_PAS_12_001}:

\begin{equation}
\left < N_{\text{cluster}} \right > = \left < N_{\text{pixel}/\text{interaction}} \right >  \left < N_{\text{interactions}} \right > \equiv \left < N_{\text{pixel}/\text{interaction}} \right > \mu
\end{equation}

where in the last step, the average number of interactions per bunch crossing, pileup, is denoted by the symbol $\mu$.

@@

\section{Luminosity calibration: van der Meer method}
In the practice, as mentioned in chapter 1, the properties of the colliding beams are not know precisely, such as the bunch density profile, so that the integral in \ref{lumi_2} cannot be solved analytically. In LHC a experimental techinque know as vdM method is implemented  with a dedicated machine setup to bring the bunch density profiles close to Guassian distributions.\\
The VdM scan method, %, exploited by S. Van der Meer for luminosity measurements at ISR  \cite{vdM_cal} and
applied by LHC Experiments in Run 1 and Run 2, allows to measure and evaluate the integral over the proton bunch densities in eq. \ref{lumi_2}. For the vdM scan method to be applicable it is also assumed that the two bunch $\rho$ can be factorized into independent terms in x and y \cite{pas-15}.  The value of the two beam overlap integrals in Eq. (2) is determined by varying the beam separation and measuring the resulting rates \cite{pas_18}:

\begin{equation}
\int \rho_{x1}(x) \rho_{x2}(x) dx = \frac{R_{x}(0)}{\int R_{x}(\Delta) d\Delta}
\end{equation}

where $R_{x}(\Delta)$ is the rate measured when the two beams are separated in x by a distance $\Delta$; a asimilar equation can be written in y. Then the beam overlap width $\Sigma_{x}$ (and similarly $\Sigma_{y}$) is defined as \cite{pas_18}:

\begin{equation}
\Sigma_{x}= \frac{1}{\sqrt{2\pi}} \frac{\int R_{x}(\Delta)d\Delta}{R_{x}(0)}
\end{equation}

yielding the final expression for luminosity (for one single bunch):

\begin{equation}
\mathcal{L}_{inst}=\frac{N_{1} N_{2}f}{2 \pi \Sigma_{x}\Sigma_{y}}
\end{equation}

where $N_{1,2}$ are the particles per bunch (bunch current) and  $f= 11246$ Hz is the bunch orbit frequency around the LHC ring.\\
This expression can be finally used in \ref{lumi_exp_gen} to get $\sigma_{vis}$:

\begin{equation}
  \sigma_{vis}=\frac{2\pi \Sigma_{x} \Sigma_{y} R(0, 0)}{N_{1}N_{2} f}
  \label{sigmavis_eq}
\end{equation}

Experimentally, two separate scans in the x and y directions are performed. The beams are scanned against each other  while measuring the rate (normalized by the product of the beam currents) at a certain number of separation steps, fitting the resulting points with a functional form, and using the fitted function to extract $\Sigma_{x,y}$ and $R(0,0)$ in \ref{sigmavis_eq}. Fig. \ref{vdm_sketch} shows an sketch of the beam positions during vdM scans in X and Y planes together with the detector rate as a function of beam separation.

\begin{center}
  \begin{figure}[ht]
    \centering
    \includegraphics[scale=.37]{Chapter3/vdm_sketch.png}
    \caption[Sketch of a vdM scan in X and Y planes and example of fitting resulting rates]{ The sketch of a vdM scan in X and Y planes. The indent sketch is an example of the fitting of the resulting rates \cite{vdM_sketch}.}
    \label{vdm_sketch}
  \end{figure}
\end{center}

%In practice, the integral in Eq. (4) is evaluated by performing two separate scans in the x and y directions, measuring the rate (normalized by the product of the beam currents) at a certain number of separation steps, fitting the resulting points with a functional form, and using the fitted function to determine the overall integral [PAS-18]. ADD HEDWING FIGURE. "this is illsutrated in fig N". Once Σx and Σy are determined, then Eq. (1) can be used to obtain the overall visible cross section σvis [pas-18].

%NOTA: Hay un pas, creo,en donde dicen lode beam current normalizado, haciendo referencia a la gráfica. Pero tal vez esto vendría en la siguiente seeción, la de resultados, ya que muestre las fitted graphs.

% https://pos.sissa.it/364/194/pdf

%DUDA: En la qe. lumi_2 decimos n_b colliding bunches y aquí hablaremos de solo un coliding buch. Lumi inst. se refiere a un solo coliding bunch? Cuál es la diferencia? En el vdM Scan usamos un solo colliding bunch?

\subsection*{Backgrounds}
Before performing the fit to extract $\Sigma_{x}$ and $\Sigma_{y}$, the raw measured rates must be corrected for background in the detector. The background contribution is estimated independently, using a special period known as Super Separation period where the beams are separated, ensuring that the only contribution is from background either beam-induced background or detector noise. There are three sources of beam-induced background: Beam Gas Elastic (BGE), Beam Gas Inelastic (BGI) and Beam Halo (BH). BGE contribution are all coherent and quasi-elastic nuclear elastic and coulomb scattering for multi-turn beam-gas interactions around the ring; typically the interaction of the primary beam proton and the aperture takes place at the collimator. BGI  are all inelastic interactions of primary beam protons with rest gas in the beam pipe. The interaction rate is dominated by the vacuum quality in the various beam line elements upstream CMS; therefore the origin of this contribution is distributed all along the long straight section. BH component is caused by the inefficiency of the main collimation system. Protons can escape from one collimator and being intercepted by another collimator \cite{bkg_source}.\\
%https://cds.cern.ch/record/1316945/files/CR2010_169.pdf
%https://cds.cern.ch/record/2816679/files/document.pdf
% Electronic noise?:
%  https://cds.cern.ch/record/1293521/files/Thesis-2002-Gu.pdf
Several other corrections are applied to the raw data before the vdM fit is performed.\\
%These corrections take into account drifts in the position of the LHC orbit, beam-beam interaction effects, and the beam separation length scale. The intensities are measured by the LHC beam current monitors and are corrected for bunched spurious (so-called “ghost” and “satellite”) charges \cite{pas_18}.

%----------- MOVE TO NEXT CHAPTER-------------%

%Before performing the fit to extract $\Sigma_{x}$ and $\Sigma_{y}$, the raw measured rates must be corrected for background in the detector. The background contribution is estimated independently, using two special periods, each 5 minutes long, during the VdM scan where the beams were separated by 6$\sigma$ (where $\sigma_{b}$ is the beam size) in both $x$ and $y$ directions, ensuring that the only contribution is from background (either beam-induced background or detector noise). The estimated background is then subtracted from the raw data before the fit is performed using a Gaussian-kind  function, which was found in 2018 to adequately describe the measured rates as a function of beam separation.\\
%Several other corrections are applied to the raw data before the VdM fit is performed. These corrections take into account drifts in the position of the LHC%orbit, beam-beam interaction effects, and the beam separation length scale. The event rates are normalized by the bunch intensities before the fit. The intensities are measured by the LHC beam current monitors and are corrected for bunched spurious (so-called “ghost” and “satellite”) charges.

%\section{Data set: 2018 vdm scan program}
%
%For 2018, the VdM scans were performed during LHC fill 6868 on June 30 and July 1 at $\sqrt{s}=13 \text{TeV}$. The LHC filling scheme used  124 colliding bunch pairs at the CMS interaction point (IP5) widely spread over the orbit to reduce long-range beam-beam effects and detector afterglow.  The resulting beam size $\sigma_{b}$ at the beginning of the fill was in the range of approximately 85–95 and 80–90 $\mu$m in x and y, respectively, increasing over time in the x dimension and decreasing over time in the y dimension. No crossing angle was used for collisions. The resulting peak pileup was approximately $\mu$ = 0.6, much lower than in a regular physics fill \cite{pas_18}.\\
%The bunch intensities were approximately 7–9$\times 10^{10}$ protons per filled bunch, resulting in a total beam intensity of slightly above $10^{10}$ protons per beam. The total beam intensities were measured with the DC Current Transformers (DCCT), and the bunch currents were measured with the Fast Beam Current Transformers (FBCT) \cite{pas_18}.\\
%To ensure a dataset with a high event count for PCC even at large beam separations, CMS gated the zero-bias triggers on 5 bunch pairs (BCIDs 265, 865, 1780, 2192, and 3380) and recorded events with a total rate of 27.7 kHz \cite{pas_18}.\\
%The CMS VdM scan program was conducted in two parts (``takes'') due to an alarm. Apart from the vdM scans other studies were carried out. Betwen that studies, only the imaging scans are used to compute $\sigma_{vis}$. The standar vdM scans are referred as ``norm'' and the imaging scans as ``img''. In the first take of the VdM scan program a vdM scan ``norm1'' and a imaging scan ``img1'' were carried out. The second part consisted of the scans ``img2'', ``img3'', ``norm2'', ``norm3'' and ``norm4'' were done. In total are 7 scans to determine $\sigma_{vis}$ \cite{pas_18}.\\
%In the vdM scans the two beams were separated by $6 \sigma_{b} \approx 600 \mu$m and scanned across one another in a sequence of 25 steps with 30 seconds per step. For the beam imaging scans  one beam (beam 1 in the first pair, followed by beam 2 in the second pair) is kept fixed at its nominal position while the other is separated and scanned in 19 steps from  $+$4.5$\sigma_{b}$ to $-$4.5$\sigma_{b}$ with 46 seconds per step. In each of both scans (scan  pairs), the scan was performed first in the x direction and then in the y direction \cite{pas_18}.\\
%Fig. \ref{scan_prog}  shows the beam positions for the two beams in the x and y directions as measured by the DOROS BPMs during the scan program, showing all scan pairs of the 2018 scan program.
%
%\begin{center}
%  \begin{figure}[ht]
%    \centering
%    \includegraphics[scale=.45]{Chapter4/2018Scanprogram.png}
%    \caption[2018 scan program]{Relative change in beam positions measured by the DOROS BPMs during the 2018 scan program for the two individual beams in the horizontal x and vertical y planes, as a function of the elapsed time from the beginning of the program. The top row shows the take 1 of the program before the alarm at CMS, while the bottom two rows show the program after the alarm \cite{pas_18}.}
%    \label{scan_prog}
%  \end{figure}
%\end{center}
%
%
